### 2014-10-31 implementation.tex
edits

\name is implemented as a shallow extension of Haskell on the Glasgow Haskell
Compiler (GHC). We utilize Template Haskell functionality to implemement static
contract classification. Our proof obligations are discharged automatically
with the help of Z3~\cite{} SMT solver. Figure~\ref{fig:impl_mod} describes the
overall system architecture. The main idea in our implementation of \name is to
offload the majority of concerns related to data management such as
replication, fault tolerance, availability and convergence to Cassandra, an
off-the-shelf eventually consistent store (called \emph{backing store} in the
sequel).

@@

While cassandra offers all-or-nothing failure semantics for multiple writes
through batching, readers may witness the initial write while the batch is in
progress. \name implements atomic visibility by exploiting shim layer causality
guarantee -- an effect is included only if all the effects if depends on are
also included.

>>>>

\name is implemented as a shallow extension of Haskell on the Glasgow Haskell
Compiler (GHC). We utilize Template Haskell functionality to implement static
contract classification. Our proof obligations are discharged automatically
with the help of Z3~\cite{} SMT solver. Figure~\ref{fig:impl_mod} describes the
overall system architecture. The main idea in our implementation of \name is to
offload the majority of concerns related to data management such as
replication, fault tolerance, availability and convergence to Cassandra, an
off-the-shelf eventually consistent store (called \emph{backing store} in the
sequel).

@@

While Cassandra offers all-or-nothing failure semantics for multiple writes
through batching, readers may witness the initial write while the batch is in
progress. \name implements atomic visibility by exploiting shim layer causality
guarantee -- an effect is included only if all the effects if depends on are
also included.
